---
output: html_document
---
# COVID-19 - INDIA ANALYSIS {.tabset}

## EXPLORATORY ANALYSIS

This RPubs documented is created to learn more about the COVID19 Confirmed Cases for India. This link will be usually shared in my personal blog i.e.; <http://www.arunkoundinya.com>. For other elated blogs request to visit my blog page and post your comment there. 

Hope you will love the analysis and also here is the source code in the github account. <https://github.com/arun0710/COVID19> Request to post your any improvement on the code for my learning to my <a href="mailto:arun7106@icloud.com">E-Mail ID</a>

### TimeSeries Interactive State-wise Map with Confirmed Cases

Hope you will loved this interactive chart on Rpubs instead on RShiny :). My Wife loved this  timline bar a lot as it is just intuitive enough to know which states have comparitvely more cases than others.
</br>
</br>
```{r echo=FALSE,fig.width=9.5,fig.height=7.5,message=FALSE,warning=FALSE,error=FALSE,eval=TRUE}
library(jsonlite)
library(leaftime)
library(htmltools)
library(leaflet)
library(rgdal)
library(reshape2)
library(readxl)
library(stringr)
library(cluster)
library(factoextra)

StatesDaily <- "https://api.covid19india.org/states_daily.json"
StatesDaily <- fromJSON(StatesDaily)
StatesDaily <- as.data.frame(StatesDaily)

TestsDaily <- "https://api.covid19india.org/state_test_data.json"
TestsDaily <- fromJSON(TestsDaily)
TestsDaily <- as.data.frame(TestsDaily)

StatesDaily<-melt(StatesDaily,id.vars = c("states_daily.status","states_daily.date"))
StatesDaily<-dcast(StatesDaily,states_daily.date + variable ~ states_daily.status )
StatesDaily$states_daily.date<-as.Date(as.character(StatesDaily$states_daily.date),format = "%d-%b-%y")
StatesDaily<-StatesDaily[with(StatesDaily, order(variable, states_daily.date)), ]
StatesDaily[,c("Confirmed","Deceased","Recovered")] <- sapply(StatesDaily[,c("Confirmed","Deceased","Recovered")],as.numeric)
StatesDaily$Confirmed_Cumsum <- ave(StatesDaily$Confirmed, StatesDaily$variable, FUN=cumsum)
StatesDaily$Deceased_Cumsum <- ave(StatesDaily$Deceased, StatesDaily$variable, FUN=cumsum)
StatesDaily$Recovered_Cumsum <- ave(StatesDaily$Recovered, StatesDaily$variable, FUN=cumsum)

StatesDaily$variable<-as.character(StatesDaily$variable)

StatesDaily$statecode<-substring(StatesDaily$variable,nchar((StatesDaily$variable))-1,nchar((StatesDaily$variable)))
StatesDaily$statecode<-toupper(StatesDaily$statecode)

LatLongMapper <- read_excel("SupportFiles/LatLongMapper.xlsx")
StatesDaily<-merge(StatesDaily,LatLongMapper,by.x="statecode",by.y="statecode",all.x=TRUE)
StatesDaily<-subset(StatesDaily,!(is.na(StatesDaily$state)))
StatesDaily$states_daily.date<-as.Date(StatesDaily$states_daily.date)
StatesDaily$start<-StatesDaily$states_daily.date
StatesDaily$end<-StatesDaily$states_daily.date
StatesDaily$radius<-(StatesDaily$Confirmed_Cumsum)/2000
StatesDaily$color<-"#0032FFFF"
StatesDaily$popup<-paste(paste("State : ",StatesDaily$state,sep = "")
                        ,paste("Confirmed : ",StatesDaily$Confirmed_Cumsum,sep = "")
                         ,paste("Deceased : ",StatesDaily$Deceased_Cumsum,sep = "")
                         ,paste("Recovered : ",StatesDaily$Recovered_Cumsum,sep = ""),sep="<br>\n")

States_Daily_Geo <- geojsonio::geojson_json(StatesDaily,lat="Lat",lon="Long")

states <- readOGR("IndiaMaps/IND_adm1.shp",verbose = FALSE)

leaflet(States_Daily_Geo) %>%
  addTiles() %>%
  setView(78.435977, 23.204480, zoom = 5) %>%
  addTimeline(width = "25%",
    timelineOpts = timelineOptions(
      styleOptions = NULL, # make sure default style does not override
      pointToLayer = htmlwidgets::JS(
        "
        function(data, latlng) {
         var popupOptions = {maxWidth: 200};
         var popupContent = data.properties.popup;
        return L.circleMarker(
        latlng,
    {
      radius: +data.properties.radius,
      color: data.properties.color,
      fillColor: data.properties.color,
      fillOpacity: 1
    }
  ).bindPopup(popupContent,popupOptions);
        }
        "
      )
    )
  ) %>%  addPolygons(data=states, weight = 2, fillColor = "green")
```


### Interactive State-wise LogScale & Linear Scale of Confirmed Cases as on Date

Below is a Linear & Log Scale Graph of the Confirmed Cases Over Time; The Log Scale Graph has became more popular to highlight the concept of flatenning the curve. If we start playing around these dropdowns we can draw more insights which state has started early corrections with preperation like Kerala.
</br>
</br>
```{r echo=FALSE,fig.width=9.5,fig.height=7.5,message=FALSE,warning=FALSE,error=FALSE,eval=TRUE}
library(plotly)

ConfirmedbyState<-dcast(StatesDaily[,c("states_daily.date","state","Confirmed_Cumsum")],states_daily.date ~ state)

cols <- names(ConfirmedbyState[,c(2:ncol(ConfirmedbyState))])

p <- plot_ly(ConfirmedbyState,
             type = "scatter",
             mode = "lines",
             x = ~as.Date(states_daily.date), 
             y= ~as.numeric(ConfirmedbyState[[cols[[34]]]]), 
             name = cols[[34]])
## Add arbitrary number of traces
## Ignore first col as it has already been added
for (col in cols[-1]) {
  p <- p %>% add_lines(x = ~as.Date(states_daily.date), y = ConfirmedbyState[[col]], name = col, visible = FALSE)
}

p <- p %>%
  layout(
    title = "Log/Linear Graph of Confirmed Cases Over Time",
    xaxis = list(title = "Date"),
    yaxis = list(title = "Confirmed Cases As on Date"),
    updatemenus = list(
      list(active=0,
           y = 1.0,
           ## Add all buttons at once
           buttons = list(
             list(label = 'linear',
                  method = 'update',
                  args = list(list(visible = c(T,F)), list(yaxis = list(type = 'linear')))),
             list(label = 'log',
                  method = 'update', 
                  args = list(list(visible = c(F,T)), list(yaxis = list(type = 'log')))))),
        
      list(active=33,
        y = 0.7,
        ## Add all buttons at once
        buttons = lapply(cols, function(col) {
          list(method="restyle", 
               args = list("visible", cols == col),
               label = col)
        })
      )
    )
  )
p
```



### Understanding the Relationship between the Tests & Confirmed Cases Over Time

Below graph communicates to us very clearly; How well Tests and Confirmed cases are correlated to a larger extend in Indian Sub-Continent.
</br>
</br>
```{r echo=FALSE,fig.width=9.5,fig.height=7.5,message=FALSE,warning=FALSE,error=FALSE,eval=TRUE}

ConfirmedbyState<-dcast(StatesDaily[,c("states_daily.date","state","Confirmed")],states_daily.date ~ state)
ConfirmedbyState<-ConfirmedbyState[,c(-10)]

TestsDaily$states_tested_data.updatedon<- as.Date(TestsDaily$states_tested_data.updatedon,format="%d/%m/%y")
TestsDaily$states_tested_data.totaltested<-as.numeric(TestsDaily$states_tested_data.totaltested)
TestsDaily<-TestsDaily[with(TestsDaily, order(states_tested_data.state,states_tested_data.updatedon)), ]
TestsDaily$Diff<-c(1,diff(TestsDaily$states_tested_data.updatedon))
TestsDaily<-subset(TestsDaily,TestsDaily$Diff!=0)

TestsDaily_Tests<-dcast(TestsDaily[,c("states_tested_data.updatedon","states_tested_data.state","states_tested_data.totaltested")],
                  states_tested_data.updatedon ~ states_tested_data.state,sum)
TestsDaily_Tests$Total<-rowSums(TestsDaily_Tests[,c(2:ncol(TestsDaily_Tests))],na.rm = TRUE)
TestsDaily_Tests<-subset(TestsDaily_Tests,TestsDaily_Tests$states_tested_data.updatedon>="2020-04-01" & TestsDaily_Tests$Total>0)
TestTill_DayBefore <- read_excel("SupportFiles/TestDaily_Test.xlsx")
TestTill_DayBefore$states_tested_data.updatedon<- as.Date(TestTill_DayBefore$states_tested_data.updatedon)
TodayTest<-subset(TestsDaily_Tests,TestsDaily_Tests$states_tested_data.updatedon==Sys.Date()-1)
YesterdayTest<-subset(TestTill_DayBefore,TestTill_DayBefore$states_tested_data.updatedon==Sys.Date()-2)

Compare<-rbind(YesterdayTest,TodayTest)
Compare<-as.data.frame(t(Compare))
Compare[,1]<-as.numeric(as.character(Compare[,1]))
Compare[,2]<-as.numeric(as.character(Compare[,2]))
Compare<-mutate(Compare, C=pmax(Compare[,1],Compare[,2]))
Compare<-as.data.frame(t(Compare))
Compare<-Compare[3,]
names(Compare)<-names(TestsDaily_Tests)
Compare$states_tested_data.updatedon<-as.Date(Compare$states_tested_data.updatedon,origin="1970-01-01")
Compare[1,1]<-as.Date(Sys.Date()-1)

TestTill_DayBefore<-subset(TestTill_DayBefore,TestTill_DayBefore$states_tested_data.updatedon<=Sys.Date()-2)

TestsDaily_TillToday<-rbind(TestTill_DayBefore,Compare)
TestsDaily_TillToday$Total<-rowSums(TestsDaily_TillToday[,c(2:36)],na.rm = TRUE)
names(TestsDaily_TillToday)<-names(TestsDaily_Tests)

rm(Compare,TestsDaily_Tests,p,TestTill_DayBefore,TodayTest,YesterdayTest,col,cols)

writexl::write_xlsx(TestsDaily_TillToday,"SupportFiles/TestDaily_Test.xlsx")
names(TestsDaily_TillToday)[2]<-names(ConfirmedbyState)[2]
names(TestsDaily_TillToday)[9]<-names(ConfirmedbyState)[9]
TestsDaily_TillToday_Incr<-data.frame(diff(as.matrix(TestsDaily_TillToday[,c(2:37)])))
names(TestsDaily_TillToday_Incr)<-names(TestsDaily_TillToday)[c(2:37)]
TestsDaily_TillToday_Incr$Date<-TestsDaily_TillToday$states_tested_data.updatedon[2:nrow(TestsDaily_TillToday)]

ConfirmedbyState<-subset(ConfirmedbyState,ConfirmedbyState$states_daily.date %in% TestsDaily_TillToday_Incr$Date)
TestsDaily_TillToday_Incr<-subset(TestsDaily_TillToday_Incr,TestsDaily_TillToday_Incr$Date %in% ConfirmedbyState$states_daily.date)
TestsDaily_TillToday_Incr<-TestsDaily_TillToday_Incr[,c(37,1:36)]

ConfirmedbyState<-melt(ConfirmedbyState,id=c("states_daily.date"))
names(ConfirmedbyState)[3]<-"ConfirmedCases"
TestsDaily_TillToday_Incr<-melt(TestsDaily_TillToday_Incr,id=c("Date"))
names(TestsDaily_TillToday_Incr)[3]<-"Tests"

PlottingFrame<-merge(ConfirmedbyState,TestsDaily_TillToday_Incr,by.x=c("states_daily.date","variable"),
                     by.y=c("Date","variable"),all.x=TRUE)

names(PlottingFrame)[2]<-"State"

PlottingFrame$Tests[is.na(PlottingFrame$Tests)]<-0
PlottingFrame$ConfirmedCases[is.na(PlottingFrame$ConfirmedCases)]<-0


fig <- plot_ly(subset(PlottingFrame,PlottingFrame$State=="Total"))
fig <- fig %>% add_trace(x = ~states_daily.date, y = ~ConfirmedCases, type = 'bar', name = 'ConfirmedCases',
                         marker = list(color = '#C9EFF9'),
                         hoverinfo = "text",
                         text = ~ConfirmedCases)

fig <- fig %>% add_trace(x = ~states_daily.date, y = ~Tests, type = 'scatter', mode = 'lines', name = 'Total_TotalTests', yaxis = 'y2',
                         line = list(color = '#45171D'),
                         hoverinfo = "text",
                         text = ~Tests)
fig <- fig %>% layout(title = 'Daily Confirmed Cases vs Daily Tests',
                      xaxis = list(title = ""),
                      yaxis = list(side = 'left', title = 'Confirmed Cases', showgrid = FALSE, zeroline = FALSE),
                      yaxis2 = list(side = 'right', overlaying = "y", title = 'Daily Tests', showgrid = FALSE, zeroline = FALSE))


fig
```


### Clusters based on Positivity Rate and Confirmed Cases

Below graph communicates to us very clearly; In Descending Order of Future HotSpot States except Maharashtra. The right most cluster indicates that the testing is not being done or reported.
</br>
</br>

```{r echo=FALSE,fig.width=9.5,fig.height=7.5,message=FALSE,warning=FALSE,error=FALSE,eval=TRUE}

PlottingFrame$PRate<-round((PlottingFrame$ConfirmedCases/PlottingFrame$Tests)*100,2)
PlottingFrame$PRate[is.infinite(PlottingFrame$PRate)]<-100
PlottingFrame$PRate[is.na(PlottingFrame$PRate)]<-0

ClusterFrame<-dcast(PlottingFrame[,c(1,2,5)], State ~ states_daily.date)
States<-ClusterFrame$State
ClusterFrame<-ClusterFrame[,c(2:ncol(ClusterFrame))]
ClusterFrame<-ClusterFrame[,c((ncol(ClusterFrame)-10):ncol(ClusterFrame))]
ClusterFrame$Avg<-rowSums(ClusterFrame)/ncol(ClusterFrame)
ClusterFrame<-as.data.frame(ClusterFrame[,"Avg"])
names(ClusterFrame)<-"Avg"
rownames(ClusterFrame)<-States

Test<-dcast(PlottingFrame[,c(1,2,4)], State ~ states_daily.date)
Test<-Test[,c(2:ncol(Test))]
Test<-Test[,c((ncol(Test)-10):ncol(Test))]
Test$Avg<-rowSums(Test)/ncol(Test)
Test<-as.data.frame(Test[,"Avg"])
names(Test)<-"Avg.Test"

ClusterFrame<-cbind(ClusterFrame,Test)

Test<-dcast(PlottingFrame[,c(1,2,3)], State ~ states_daily.date)
Test<-Test[,c(2:ncol(Test))]
Test<-Test[,c((ncol(Test)-10):ncol(Test))]
Test$Avg<-rowSums(Test)/ncol(Test)
Test<-as.data.frame(Test[,"Avg"])
names(Test)<-"Avg.Conf"


ClusterFrame<-cbind(ClusterFrame,Test)
ClusterFrame$State<-rownames(ClusterFrame)

ClusterFrame<-subset(ClusterFrame,ClusterFrame$State!="Total")
ClusterFrame<-subset(ClusterFrame,ClusterFrame$State!="Maharashtra")

hc.cut<-hcut(ClusterFrame[,c(1,3)],k=7,hc_method = "ward.D2")
fviz_cluster(hc.cut,ellipse.type = "convex",geom="text",xlab="Positivity Rate",ylab="Confirmed Cases",ggtheme = theme_gray(),main = "Cluster Plot - Future Hotspots in Desc.")

```

## PREDICTIVE ANALYSIS

This RPubs documented is created to learn more about the COVID19 Confirmed Cases for India. This link will be usually shared in my personal blog i.e.; <http://www.arunkoundinya.com>. For other elated blogs request to visit my blog page and post your comment there. 

Source code will not be uploaded into the github account for this tab. Request to post your any improvement for my learning to my <a href="mailto:arun7106@icloud.com">E-Mail ID</a>

### Basic TimeSeries Forecasting on Tests with Regression on Confirmed Cases

As we learnt in India Scenario that more the tests more the confirmed cases. This is a base model which uses time-series forecasting model on Tests and then the output of tests is regressed to get the total confirmed cases.
</br>
</br>


```{r echo=FALSE,fig.width=9.5,fig.height=7.5,message=FALSE,warning=FALSE,error=FALSE,eval=TRUE}

RecoveredTotal<-subset(StatesDaily,StatesDaily$state=="Total")

RecoveredTotal<-subset(RecoveredTotal,RecoveredTotal$states_daily.date %in% TestsDaily_TillToday_Incr$Date)

PlottingFrame<-merge(ConfirmedbyState,TestsDaily_TillToday_Incr,by.x=c("states_daily.date","variable"),
                     by.y=c("Date","variable"),all.x=TRUE)

names(PlottingFrame)[2]<-"State"

ForecastingFrame<-subset(PlottingFrame,PlottingFrame$State=="Total")
ForecastingFrame<-merge(ForecastingFrame,RecoveredTotal[,c(2,6,7,8,9)],by.x="states_daily.date",by.y="states_daily.date",all.x=TRUE)
ForecastingFrame$ActiveCases_SoFar<-ForecastingFrame$Confirmed_Cumsum-ForecastingFrame$Deceased_Cumsum-ForecastingFrame$Recovered_Cumsum

rm(ClusterFrame,ConfirmedbyState,fig,hc.cut,LatLongMapper,PlottingFrame,RecoveredTotal,states,StatesDaily,Test,
   TestsDaily,TestsDaily_TillToday,TestsDaily_TillToday_Incr,States_Daily_Geo,States)

library(forecast)

##Considering Upper Confidence Interval for Tests
FutureTests<-as.data.frame(forecast(auto.arima(ForecastingFrame$Tests),15)$upper[,2])
names(FutureTests)[1]<-"Tests"

model<-lm(ConfirmedCases ~ Tests, ForecastingFrame)

FuturePlotFrame<-data.frame(ConfirmedCases=predict(model,newdata = FutureTests))
FuturePlotFrame$ConfirmedCases<-round(FuturePlotFrame$ConfirmedCases,0)
FuturePlotFrame$TotalConfirmedCases<-ave(FuturePlotFrame$ConfirmedCases, FUN=cumsum)+ForecastingFrame$Confirmed_Cumsum[nrow(ForecastingFrame)]
FuturePlotFrame$RecoveredCases<-round(as.numeric(forecast(auto.arima(ForecastingFrame$Recovered),15)$lower[,1]),0)
FuturePlotFrame$RecoveredCases_Cumsum<-ave(FuturePlotFrame$RecoveredCases, FUN=cumsum)+ForecastingFrame$Recovered_Cumsum[nrow(ForecastingFrame)]
FuturePlotFrame$Deaths<-round(as.numeric(forecast(auto.arima(diff(ForecastingFrame$Deceased_Cumsum)),15)$upper[,2]),0)
FuturePlotFrame$TotalDeaths<-ave(FuturePlotFrame$Deaths, FUN=cumsum)+ForecastingFrame$Deceased_Cumsum[nrow(ForecastingFrame)]
FuturePlotFrame$ActiveCases<-FuturePlotFrame$TotalConfirmedCases-FuturePlotFrame$TotalDeaths-FuturePlotFrame$RecoveredCases_Cumsum
FuturePlotFrame$Date<-seq(Sys.Date(),Sys.Date()+14,by=1)
FuturePlotFrame$ProbableHospitalCases<-round(FuturePlotFrame$ActiveCases*0.30,0)
Fif_DayResult<-data.frame(Resulsts_15Days=t(FuturePlotFrame[15,])[c(8,2,7,6,9),])

fig <- plot_ly(FuturePlotFrame, x = ~Date, y = ~TotalConfirmedCases, name = 'ConfirmedCases', type = 'scatter', mode = 'lines+markers') 
fig <- fig %>% add_trace(y = ~ActiveCases, name = 'Active Cases', mode = 'lines+markers') 
fig


```

Active Caes, Total Confirmed Cases, Total Deathson 15th day starting from today. As a rule based of current Asympotomatic, Mild Cases upon Hospitalized Cases. Required Hospitalized cases can be calculated as 30% of total Active Cases considering the same recovery rate for even hospitalized cases.
<br>
<br>

```{r echo=FALSE,fig.width=9.5,fig.height=7.5,message=FALSE,warning=FALSE,error=FALSE,eval=TRUE}

library(htmlTable)
htmlTable(Fif_DayResult,
          header =  paste(c("Results_15thDay_"), "FromToday"),
          rnames = paste(c("Date", "ConfirmedCases_Total",
                           "ActiveCases", "Deaths_Total","Hospitalized People"), "_15thDay"),
          caption="Base Model Forecasting Summary on 15th Day from Today",
          tfoot="&dagger; Hospitalized People are asummed as 30% of Actice Cases")


```

### SIRS Model with Undected Cases with revised transmission probability

Initial parameters for the SIRS Model for the suspected pouplation is kept for all urban & metro cities and then by past trend it is seen that the testing is 20 times lower than expected. As SIRS Model is being considered as over optimistic the initial set variables play a huge role in terms of arriving at the Infected Inviduals. 

Also, Active Cases is arrived as the present recovery trend instead to use SIRS Model.

Note: There might be few changes as we learn during the pandemic course. The suggested model would certainly undergo changes on weekly basis.

</br>
</br>


```{r echo=FALSE,fig.width=9.5,fig.height=7.5,message=FALSE,warning=FALSE,error=FALSE,eval=TRUE}

sir_1 <- function(beta, gamma, S0, I0, R0, times) {
  require(deSolve) # for the "ode" function
  
  # the differential equations:
  sir_equations <- function(time, variables, parameters) {
    with(as.list(c(variables, parameters)), {
      dS <- -beta * I * S
      dI <-  beta * I * S - gamma * I
      dR <-  gamma * I
      return(list(c(dS, dI, dR)))
    })
  }
  
  # the parameters values:
  parameters_values <- c(beta  = beta, gamma = gamma)
  
  # the initial values of variables:
  initial_values <- c(S = S0, I = I0, R = R0)
  
  # solving
  out <- ode(initial_values, times, sir_equations, parameters_values)
  
  # returning the output:
  as.data.frame(out)
}

contact_rate = (FuturePlotFrame$ConfirmedCases[1]*20)/10000000 # number of contacts per day
transmission_probability = sum(ForecastingFrame$ConfirmedCases)*3/sum(ForecastingFrame$Tests)   # transmission probability
infectious_period = 21          # infectious period

sir_values_1<-sir_1(beta = contact_rate*transmission_probability, gamma = 1/infectious_period,
                    S0 = (30-(ForecastingFrame$Confirmed_Cumsum[nrow(ForecastingFrame)]*20)/10000000), 
                    I0 = (ForecastingFrame$Confirmed_Cumsum[nrow(ForecastingFrame)]*20)/10000000
                                   , R0 = (ForecastingFrame$Recovered_Cumsum[nrow(ForecastingFrame)]*20)/10000000,
                    times = seq(0, 40))


sir_values_1$TotalConfirmedCases<-(sir_values_1$I*10000000)/20
sir_values_1$RecoveredCases<-c(round(as.numeric(forecast(auto.arima(ForecastingFrame$Recovered),15)$mean),0),round(as.numeric(forecast(auto.arima(ForecastingFrame$Recovered),26)$upper[,1]),0))
sir_values_1$RecoveredCases_Cumsum<-ave(sir_values_1$RecoveredCases, FUN=cumsum)+ForecastingFrame$Recovered_Cumsum[nrow(ForecastingFrame)]
sir_values_1$Deaths<-round(as.numeric(forecast(auto.arima(diff(ForecastingFrame$Deceased_Cumsum)),41)$upper[,2]),0)
sir_values_1$TotalDeaths<-ave(sir_values_1$Deaths, FUN=cumsum)+ForecastingFrame$Deceased_Cumsum[nrow(ForecastingFrame)]
sir_values_1$ActiveCases<-sir_values_1$TotalConfirmedCases-sir_values_1$TotalDeaths-sir_values_1$RecoveredCases_Cumsum
sir_values_1$TotalConfirmedCases<-round(sir_values_1$TotalConfirmedCases,0)
sir_values_1$ActiveCases<-round(sir_values_1$ActiveCases,0)
sir_values_1<-sir_values_1[-1,]

sir_values_1$Date<-seq(Sys.Date(),Sys.Date()+39,by=1)
sir_values_1$ProbableHospitalCases<-round(sir_values_1$ActiveCases*0.30,0)

Fif_DayResult<-cbind(data.frame(Resulsts_15Days=t(sir_values_1[15,])[c(11,5,10,9,12),]),data.frame(Resulsts_15Days=t(sir_values_1[30,])[c(11,5,10,9,12),]),data.frame(Resulsts_15Days=t(sir_values_1[40,])[c(11,5,10,9,12),]))


fig <- plot_ly(sir_values_1, x = ~Date, y = ~TotalConfirmedCases, name = 'ConfirmedCases', type = 'scatter', mode = 'lines+markers') 
fig <- fig %>% add_trace(y = ~ActiveCases, name = 'Active Cases', mode = 'lines+markers') 
fig


```
<br>
<br>
Quicky Summary on 15th, 30th & 40th Day Prediction for easy readability.
<br>
<br>

```{r echo=FALSE,fig.width=9.5,fig.height=7.5,message=FALSE,warning=FALSE,error=FALSE,eval=TRUE}

library(htmlTable)
htmlTable(Fif_DayResult,
          header =  paste(c("Results_15thDay_","Results_30thDay_","Results_40thDay_"), "FromToday | "),
          rnames = paste(c("Date", "ConfirmedCases_Total",
                           "ActiveCases", "Deaths_Total","Hospitalized People"), ""),
          caption="Adjusted SIRs Model Forecasting Summary on nth Day from Today",
          tfoot="&dagger; Hospitalized People are asummed as 30% of Actice Cases")


```
<br>

Thanks a lot,
Arun Koundinya
<br>

